\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{amsfonts}
\usepackage{hyperref}

\geometry{a4paper, margin=1in}

\title{Python Web Developer Roadmap}
\author{}
\date{}

\begin{document}

\maketitle

\section*{🐍 Python Web Developer Complete Checklist}

\subsection*{1️⃣ Python Fundamentals}
Learn the basics of Python.

\begin{itemize}[label=$\square$]
    \item Install Python and set up environment
    \item Variables and data types
    \item Numbers and strings
    \item Lists, tuples, sets, dictionaries
    \item Conditional statements (if, elif, else)
    \item Loops (for, while)
    \item Functions
    \item Lambda functions
    \item Modules and packages
    \item File handling
    \item Error handling (try, except)
    \item Object-Oriented Programming (OOP)
    \item Virtual environments (venv)
\end{itemize}

\subsection*{🌐 Web Fundamentals}
Understand how the web works.

\begin{itemize}[label=$\square$]
    \item Basics of HTML
    \item Basics of CSS
    \item Basics of JavaScript
    \item How browsers work
    \item HTTP / HTTPS protocol
    \item Request vs Response
    \item GET / POST / PUT / DELETE methods
    \item Status codes (200, 404, 500)
\end{itemize}

\subsection*{🔧 Version Control}
Learn version control using Git.

\begin{itemize}[label=$\square$]
    \item Install Git
    \item \texttt{git init}
    \item \texttt{git add}
    \item \texttt{git commit}
    \item \texttt{git push}
    \item \texttt{git pull}
    \item Branches
    \item Merge conflicts
    \item Use GitHub
\end{itemize}

\subsection*{🗄️ Databases}
Learn SQL databases.

\begin{itemize}[label=$\square$]
    \item Install PostgreSQL or MySQL
    \item Database basics
    \item Tables and columns
    \item Primary and foreign keys
    \item SQL queries (SELECT, INSERT, UPDATE, DELETE)
    \item JOIN queries
    \item Indexes
    \item Database relationships
    \item Use SQLite for small apps
\end{itemize}

\subsection*{⚙️ Python Web Framework}
Learn a framework.

\subsubsection*{Flask}
\begin{itemize}[label=$\square$]
    \item Install Flask
    \item Routes
    \item Templates (Jinja2)
    \item Forms
    \item Database integration
    \item REST API with Flask
\end{itemize}

\subsubsection*{Django}
\begin{itemize}[label=$\square$]
    \item Install Django
    \item Django project structure
    \item Models
    \item Views
    \item Templates
    \item Django ORM
    \item Authentication system
    \item Django Admin panel
\end{itemize}

\subsubsection*{FastAPI}
\begin{itemize}[label=$\square$]
    \item Install FastAPI
    \item Create API endpoints
    \item Request validation
    \item Response models
    \item Async APIs
\end{itemize}

\subsection*{🔌 APIs}
Learn to build and test APIs.

\begin{itemize}[label=$\square$]
    \item Understand REST APIs
    \item JSON format
    \item CRUD operations
    \item API authentication
    \item API documentation
    \item Test APIs with Postman
\end{itemize}

\subsection*{🧪 Testing}
Test your applications.

\begin{itemize}[label=$\square$]
    \item Unit testing
    \item Install PyTest
    \item Write test cases
    \item Test API endpoints
\end{itemize}

\subsection*{🐳 Deployment \& DevOps}
Learn how to run apps online.

\begin{itemize}[label=$\square$]
    \item Linux basics
    \item Environment variables
    \item Install Docker
    \item Containerize your app
    \item Deploy on Amazon Web Services
    \item Deploy on DigitalOcean
\end{itemize}

\subsection*{🧠 Advanced Backend Topics}
Important for professional developers.

\begin{itemize}[label=$\square$]
    \item Authentication (JWT)
    \item Authorization
    \item WebSockets
    \item Background tasks
    \item Caching with Redis
    \item Task queues with Celery
    \item Security best practices
\end{itemize}

\subsection*{💻 Projects}
Build real projects.

\begin{itemize}[label=$\square$]
    \item Todo App
    \item Blog Website
    \item REST API service
    \item Chat application
    \item E-commerce backend
    \item Authentication system
    \item Social media app
\end{itemize}

\subsection*{📂 Portfolio}
Show your work.

\begin{itemize}[label=$\square$]
    \item Upload projects to GitHub
    \item Write README documentation
    \item Deploy projects online
    \item Create portfolio website
\end{itemize}

\subsection*{💼 Job Preparation}
Get ready for developer jobs.

\begin{itemize}[label=$\square$]
    \item Practice coding challenges
    \item Prepare backend interview questions
    \item Build 5–10 strong projects
    \item Apply on LinkedIn
    \item Apply on Indeed
\end{itemize}

\end{document}
